\documentclass[12pt]{article}
\usepackage{setspace}
\begin{document}

	\paragraph{6.19}
		\subparagraph{1}
			The men, as much money as they have recieved from wives in the name of dowry, so much they join with the dowry from their own goods, an estimation having been made.
		\subparagraph{2}
			An account is kept of all this money together, and the profits are reserved: which ever of them will have survived [the other] in life, the portion of both with the profits of earlier times goes to that one.
		\subparagraph{3}
			The man have over their wives, just as over their children, the power of life and death; and when the father of a family born in a more illustrious place has died, his relations come together and, if the thing has come into suspicion about, they have a questioning about his death of his wives in slavish manner and, if something has been found out, after they have been tortured with fire and all torments, they kill them.
		\subparagraph{4}
			The funerals are magnificent and sumptuous for the culture of the Gauls, and all things which they judge to have been dear to the living, they cast into the fire, even animals, and shortly before this memory, the slaves and clients whom it was agreed to have been dear to them, were cremated together, with the proper funeral rites having been completed.

	\paragraph{7.77}
		\subparagraph{1}
			But those, who were being beseiged at Alesia, with the day having passed, on which they had awaited the help of their own, all the grain having been consumbed, unsure of what was happening among the Aedui, council having been assembled,
		\subparagraph{2}
			they were deliberating about the outcome of their fortunes. And with various opinions having been expressed among them, a part of with were recomending a surrende, a part, bursting out while their forces lasted, it seems the speech of Critognatus should not be passed over because of its singular and nefarious cruelty.
		\subparagraph{15}
			What else do the Romans truly seek or what do they want, except led along by greed, to settle in the states and fields of these whom they have learned by fame are noble and powerful in war, and to impose perpetual slavery on them? For they have not waged wars on any other condition.
		\subparagraph{16}
			For if you do not know those things which are being done in distant nations, consider our nearest neighbour Gaul, which having been reduced to a province, its justice and laws having been changed, having been subjected to the axes is oppressed by perpetual with the justice having been reduced to a province, and with the laws having been altered, subjected to axes, is pressed by perpetual slavery."

	\paragraph{7.78}
		\subparagraph{1}
			The opinions having been spoken, they decide that those
			who by health or age are useless for war should depart
			from the town and all things should be tried before they
			descend to the recommendation of Critognatus:
		\subparagraph{2}
			However they must use that advice, if the matter compels
			[it] and supports delay, rather than that a condition of
			surrender or peace should be endured.
		\subparagraph{3}
			The townspeople, who had recieved them in the town, are compelled to exit with children and wives. These, when they had approached to the fortifications of the Romans,
		\subparagraph{4}
			weeping, prayed with all entreaties that having been
			recieved into slavery, they [the Romans] relieve them
			with food.
		\subparagraph{5}
			But Caesar, with gaurds having been posted on the wall, was prohibiting them to be recieved.

	\paragraph{7.79}
		\subparagraph{1}
			Meanwhile, Commius and the other leaders, to whom
			highest of imperium had been assigned, arrive with all forces
			at Alesia, and with the hill outside having been occupied, they settled not farther than 1000 paces from our fortifications.
		\subparagraph{2}
			On the next day, with the cavalry having been lead out of the camp, all that plain, which we have shown to extend 3000 paces in length, they fill and they ___
		\subparagraph{3}
			There was a view from the town of Alesia onto the field.

\end{document}
